---
title: "Commandline Histories"
warning: false
---



```{r load_libraries}
#| echo: false
library(tidyverse)
library(DT)
library(ggwordcloud)
```

```{r load_files}
#| echo: false
source("/home/someone/Desktop/Programming + Markup/R/Data-Visualisations/Wordclouds/command_wordcloud.R")
# this yields variables tf_hist intended for a dt-table and
# sorted_hist for wordcloud2
source("/home/someone/Desktop/Programming + Markup/R/Data-Visualisations/Lists/ordered_list.R")
```

Logging, in my opinion, or getting knowledge out of a big amount of information is one of the most important skills in IT. I feel like I've noticed a lot of things coming down to good documentation about what's being done in order for you not to have almost the exact same effort the next time you're doing it, considering it's a while.

# What commands have I used the most?


I use the bash `history` command quite a lot to find commands I've used before and it helps me getting to solutions a lot faster for things I've done before, but don't quite remember. Thinking about this I got curious about stuff like "Which commands have I used the most?", "What are the most pipes I've used?" or "Which command is most probable to preceed / follow a pipe?". First one I'll answer now:


::: {.panel-tabset}


## wordcloud

```{r ggwordcloud}
set.seed(42)
filtered_hist <- filter(sorted_hist, freq>20)
ggplot(filtered_hist, aes(label = command, size = freq, color = freq)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size=50) +
  theme_minimal() +
  scale_color_gradient(low = "blue", high = "darkcyan")
```

## table
```{r dt}
table <- datatable(tf_hist, options = list(order = list(2, 'desc')))
table
```

:::


While a wordcloud looks quite nice it's not the best in most cases to communicate information in a cohesive way. Therefore we'll have an interactively sortable table as well

That length, however, means that we'll have to use tools to get our wanted info and can't just count. I'll use `awk, sort, uniq` and pipes (`|`) for that matter.

`history | awk '{print $2}'` will show us all the commands that are the first word of a command invocation. Not sorted, nor counted though, but
`history | awk '{print $2}' | sort | uniq | sort -n` does the rest.


With quarto and R that's all that is needed to make those graphics from that and in result this document.
